Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-18 chi2012.tex
a  few more

Although not included in the table above, we also examined enumerated values for a number of the data sources above.  Field even as simple as ``Gender'' often disagreed in the

>>>>

Although not included in the table above, we also examined the consistency in enumerated type ranges across data sources above.  Ranges of enumerated types for properties as seemingly simple as ``Gender'' disagreed among social networks; while Facebook allowed only ``Male'' and ``Female'' for values, Google+ included a third option,``other''.  ``Relationship status'' was another for which a majority of the values had correspondences between platforms but there wer a number of unique values not present in the rest.
